Agile Testing Four Page Draft

### 2013-10-27 Paper_Draft.tex
6 Paper draft, working on TDD definition currently in section 2.

\section{Introduction}
When it comes to software development perhaps one of the most important and time consuming processes is that of software testing.  In fact, some early studies on software testing estimated that software testing could consume fifty percent or more of development costs for a product ~\cite{Bertolino;2007}.  because of this business's over time have become increasingly interested in attempting to optimize testing to reduce development costs.

During the 1990's \mycomment{note this is a guess, double check this!} businesses focused on using heavily regimented coding practices that was very process oriented.  Common code methods therefore tended to follow what was called a waterfall model where products were produced by running through a series of phases (IE first there was the planning phase, then designing phase
occurred, and then once the product was designed the testing phase would occur to make sure the product was customer ready. This type of design often encouraged a test last methodology which predominated this era.

In the early 2000's though critics of the heavily regimented coding practices produced a new set coding practices that focused not on heavily regimented coding practices but on more spontaneous and reactive coding practices.  These new coding practices are referred to as "agile" coding practices after the agile manifesto written in (need date here) which highlights many of the main tenets of this new style of coding.  In this new style of coding test last methodologies became less useful because agile methodologies believed that testing should occur while the code was being written, not after.  This gave rise to a new testing strategy called test first testing or Test Driven Development (TDD).

Currently there is much debate in the testing world about whether or not test first testing or test last testing is superior and what advantages one type of testing may offer over the other.  The goal of this paper is to therefore attempt to resolve this debate as much as possible by analyzing research data in the field concerning the advantages and disadvantages of each of these testing methods.  Also because research often lags behind current implementations and the field of agile development is currently changing due to its relatively new implementation this paper also plans to look into where new agile ideas are going and compare that to the research given in order to give the best possible representation of the two differing fields.  This paper will therefore discuss the advantages and disadvantages of TDD testing versus waterfall testing and explore new emerging agile methodologies in an attempt to determine the usefulness of each methodology.

In order to accomplish this we have divided the rest of the paper into four additional sections which will take about the specific ideas above in more detail. In section two of the paper we will discuss what software testing is in the context of this paper and two popular ways of implementing it, test first and test last testing.  In section three we will provide an analysis of the data explaining the potential advantages and disadvantages of TDD compared to Waterfall testing.  In section four we will go over new TDD based testing methodologies and in section five we will state our conclusions.

\section{Background}
\subsection{Software Testing}
Software testing, simply defined, is a branch of software engineering that's main purpose is to either identify potential malfunctions or to demonstrate functionality in a software system by observing the software systems execution ~\cite{Bertolino:2007}.  A simple example of this is running your code after you write it to see if it works. \mycomment{this example needs work}  The main purpose of software testing is that of increasing code quality of software products and is used in tandem with software development techniques to produce serviceable code. Although the purpose of software testing is fairly straight forward (to improve code performance) the understanding on how to best achieve this goal for any given situation can be extraordinarily complex ~\cite{Bertolino:2007}. \mycomment{this transition needs some serious help}  Due to this complexity various methodologies and beliefs currently exist on how to best test products.  In this paper our goal will be to compare various testing methodologies.

\mycomment{this transition between these two paragraphs is rather rocky}

It is important to note that there is no one standard quantitative measurement for code quality because it is a qualitative measurement.  Because of this many different types of measurement are used to attempt to prove that one testing methodology is better then another.  Although there are many different attributes that applicable for arguing the superiority of one methodology over another this paper will only focus on four attributes that are commonly found throughout research; code coverage, time efficiency, customer satisfaction, and code correctness. \mycomment{I'm not sure this paragraphs approach is the best way to get the information I want across to the reader, I probably should probably put more detail into each of my four attributes}

\mycomment{may need to add a small bit about functional testing vs unit testing for section 4}

\subsection{Testing Methods}
In this paper we will be mainly focusing on two different testing domains, waterfall/test last testing and TDD or test first a popular agile testing method.

Waterfall or test last testing is currently a very popular testing method and is usually the first way of testing that people implement.  This method follows the basic principle of a person first writes their code and then proceeds after the code is considered initially implemented to write tests that check the functionality of their code.  The developer then runs the test against the code and changes the code until the code passes the developers tests.  This testing is often used with plan based development or testing on the fly because it allows the developer to only have to write tests about parts of the code he or she is worried about. \mycomment{This paragraph needs some serious clean up and much more detail on the topic but for now it gets the basic point across}

TDD or Test first testing is another popular testing method and is primarily used in the agile community.  This follows the basic principles that one should actually write tests before code and tailor the code to the tests instead of tailoring the tests to the code.  The idea behind this testing style is that by doing this one can write their codes objectives in tests so that your code becomes tailored to your objectives instead of objectives being tailored to your code.  \mycomment{again this paragraph needs some serious clean up and detail but for now it gets the basic point across}

\mycomment{things to add to this section}

-Add a brief history to each section

-Add justification for why TDD is agile or why TDD is used as an agile practice

-Use a more specific TDD example by using extreme programming

-write a brief conclusion paragraph containing:

-That TDD and waterfall testing are vague terms and not specific

-Mention that there will also be a focus Evolved TDD forms briefly(BDD, ATDD)

>>>>

\section{Introduction}
When it comes to software development, perhaps one of the most important and time consuming processes is software testing.  In fact, some early studies on software testing estimated that it could consume fifty percent or more of development costs for a product ~\cite{Bertolino;2007}.  because of this businesses over time have become increasingly interested in attempting to optimize testing to reduce development costs.

Although there are many testing methods that currently exist two particular testing methods are currently very popular: test-last testing and test-first testing.  Test-last testing, used mostly in process oriented development, is a testing method where testing is done after the software code has been written to ensure that the code works correctly.  Test-first testing, used mostly in interval or sprint oriented development, is a testing method where testing is done before the software code is written to ensure that the future code meets certain requirements.

Currently, there is much debate in the testing community about whether or not test first or test last testing is superior.  The goal of this paper is to attempt to give an overview of the current state of this debate by analyzing current research data concerning the advantages and disadvantages of each of these testing methods.  Also because research often lags behind current implementations and the field of test first testing is currently changing due to its relatively new implementation this paper will also explore where new test first methods are going and compare them to the research given.  This paper will therefore discuss the advantages and disadvantages of test first testing versus test last testing and explore new emerging test-first methodologies in an attempt to determine the applicability of each methodology.

The rest of the paper is divided into four sections which will discuss the specific ideas above in more detail. In section two of the paper we will discuss what software testing is and current software development models with their supporting testing methods: test-first and test-last testing.  In section three we will provide an analysis of the data explaining the potential advantages and disadvantages of test first testing compared to test last testing.  In section four we will go over new test first based testing methodologies and in section five we will state our conclusions and suggestions for further research in the field.

\section{Background}
\subsection{Software Testing}
Software testing, simply defined, is a branch of software engineering that entails a series of practices meant to either identify potential malfunctions or demonstrate functionality in a software system ~\cite{Bertolino:2007}.  Software testing can be as simple as running a program to see its results or can be as complex as writing code to simulate scenarios in the real world.

When it comes to judging the effectiveness of certain testing methods it is important to note that there is no one standard quantitative measurement.  Because of this many different types of measurement are used to attempt to prove that one testing methodology is better then another.  Although there are many different attributes that are used for arguing the superiority of one method over another we will only focus on three attributes that are commonly found throughout research; code coverage, time, and code correctness.  Code coverage refers to how many lines of code percent-wise are currently being tested. For example, if I write a test with 70\% test coverage it means that 70\% of the lines of code I wrote are being tested.  Time simply means how long it takes to write or run the actual tests.  Code correctness refers to how many errors are found within code after it is considered finished.  These three attributes are popular to use because they can be quantitatively measured and are considered important within the testing community.

\subsection{Waterfall Development and Testing}

From as early as the 1970s a popular software development model was the waterfall model where software was developed in a series of phases.  The waterfall method has been a popular development model because it is considered simple to implement correctly and is also considered to be time efficient because completing previous phases helps latter phases become more efficient. The first phase in the standard waterfall model was the requirements phase where requirements were set by the customer or design company.  Next the design phase occurred where the product was designed which was then followed by the implementation phase where the product was actually created.  The final phase of the development phase was then the verification phase where testing and debugging occurred \mycomment{wikipedia waterfall model}.  Due to the fact that these processes often put testing at the end of development, a certain type of testing method, the test-last method, became very popular to use with the waterfall development method.

Test last testing is currently a popular testing method and is usually the first testing method that people tend to implement.  Test Last testing is the practice of writing tests after code has been written that check the functionality of their code.  These tests are then used to check the written code for any potential errors which are then fixed by the developer until no errors are found by the tests.  Test last testing is considered simple to implement and can allow the programmer to focus on writing tests based on areas of his code that he may be concerned about.

\subsection{Agile Oriented Development and Testing}

In the late 1990s some software developers started to criticize the sequence-oriented waterfall model, complaining that it was too brittle and inflexible to meet the demands of the standard customer.  In response to these critiques of the waterfall model a new model for developing software emerged, the agile development model.  This new development model, based on the tenets of the agile manifesto \mycomment{cite manifesto here!}, promoted the idea that all actions of development should not occur in an ordered sequence but in a series of time-boxed iterations where in each iteration setting requirements, design, implementation and testing would occur simultaneously.  The goal of each iteration is to produce a demonstrable working product to show a customer and receive feedback on the product.  Some current development practices that are considered agile are Extreme Programming and Scrum.

Due to the changes in Agile programming test-last testing was pushed aside in favor of a new style known as test-first testing.  In 1996 \mycomment{might be 2001} with the release of the agile development practice Extreme Programming, the idea of test first testing, implemented in test driven development, started to become popular for the first time ~\cite{Hammond:2012}. Test-first testing is the practice of writing tests before code has been written and then writing code to make the tests pass.  It should be noted that since tests occur before development test-first testing tends to be heavily linked to development methods and thus the most common test-first models also include development elements as well.

The most well known and most used test-first model is that of test driven development or TDD for short.  In its current use in the field the phrase TDD is mostly used as a blanket term for any sort of development practice that uses test-first testing to drive code development. That being said it is important to note that although TDD has been turned into a vague term in this paper we will focus more on its original specific definition.
